### 2014-02-24 paper/concrete.tex
Note that the lemma is not a real reference.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
Other stuff.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

    Next, suppose we have a language $L'$ with machine states $|Q|$,
    evaluation relation $|.->|'$ and erasure function $e'$.  Given
    functions $f^{-1} : |C -> Q|$ and $f : |Q -> C|$ relating machine
    states between $L$ and $L'$, obeying the condition $f^{-1} \circ f =
    id$.  Then to show termination sensitive non-interference for $L'$,
    it suffices to show that for every evaluation rule $|Q| |.->|' |Q'|$
    it is either the case that $f(|Q|) |.->| f(|Q'|)$ or that
    \ldots
\end{theorem}

\begin{proof}
Our proof proceeds along the same lines as a traditional TSNI proof.
\ldots (wait for the proof to be done)
\end{proof}

>>>>

    Next, suppose we have a language $L'$ with machine states $|Q|$,
    evaluation relation $|.->|'$ and erasure function $e'$.  Given
    functions $f^{-1} : |C -> Q|$ and $f : |Q -> C|$ relating machine
    states between $L$ and $L'$, obeying the condition $f^{-1} \circ f =
    id$ and $f^{-1} \circ e' \circ f = e$.  Then to show termination sensitive non-interference for $L'$,
    it suffices to show that for every evaluation rule $|Q| |.->|' |Q'|$
    it is either the case that $f(|Q|) |.->| f(|Q'|)$ or that
    \ldots
\end{theorem}

\begin{proof}
Our proof proceeds along the same lines as a traditional TSNI proof,
we simply must show \Red{Lemma~1} holds for our language.  We proceed by induction
over reduction derivations in the first step.
\end{proof}
